---
title: Stop thinking, start simulating
author: Ezra Citron
date: '2021-03-23'
slug: let-simulation-be-a-substitute-for-thinking
categories: []
tags: []
---

My mother is a keen reader of 'the daily scientist', a UK based popular sceince magazine. Invariably over a given weekend she'll exclaim something along the lines of "The last estimate was wrong, the observable universe is 245,600,00 years old, not 245,700,00" or "carrots have been proven to make you totally immune to cancer", ill take an interest but quickly return to my book (/phone). 

so here it is


_"Dog breeder Harriet Hound’s prize pooch has just had 10 puppies. She is particularly pleased, because there are only nine puppies in the latest litter of her arch-rival, Matilda Mutt. _

_However, for Harriet, it isn’t just the overall quantity that counts, it is the number of female puppies, because females earn her a premium. On average, 50 per cent of puppies are female. “What is the chance I’ve got more female puppies than Matilda?” wonders Harriet._

_You might think she needs to use sophisticated probability maths to work this out, but in fact there is a way to figure out the solution with some relatively simple reasoning."_

I thought about it, scratched by beard and thought about it some more, but at no point did any inspration come to me, and by the the _relatively simple reasoning_ they talked about it the question seemed more like a taunt than anything else.

## Time to stop thinking and start simulating

Though this would be a good opportunity to break the question down one step at a time and solve it by brute force simply using simulation.

Lets make a function that simulates both harriet and matilda dogs giving birth. we have one argument `number_of_dogs`, because the only difference between harriet and marilda in the nubmer of puppies each of their respective dogs have.

```{r}

create_pups <- function(number_of_dogs) {
    sample(x = c("Male","Female"),replace = T,prob = c(0.5,0.5),size = number_of_dogs)
}


```

now we can run the function to see how many male a female dogs were bred
```{r}
set.seed(123)
create_pups(9)

```

Harriet had 6 Males, 3 Females, great

```{r}
create_pups(10)
```
and Matilda had 4 Males and 6 Females. 

Hang on! We only did this once, we'd get a different number if we were to do it again. hmm..

This is where simulation comes it, we could run this 100 times, each time record whether Harriet or matilda had more females. At the end say Harriet has more females 54 times, and Matilda 46 times, then we could say that there is a 54% chance that Harriet has more dogs. 


```{r}

library(tidyverse)
number_of_sims <- 1000
sim <- tibble(event = 1:number_of_sims)

sim <- sim %>% rowwise() %>%
  mutate(
    outcome_10_dogs = list(create_pups(10)) ,
    outcome_9_dogs = list(create_pups(9)),
    Matilda_female = sum(outcome_10_dogs == "Female"),
    Harriet_females = sum(outcome_9_dogs == "Male")
  ) %>% ungroup()

sim %>%
  mutate(
    winner =
      case_when(
        Harriet_females == Matilda_female ~ "equal",
        Matilda_female > Harriet_females ~ "Matilda",
        Harriet_females > Matilda_female ~ "Harriet")) %>%
  count(winner) %>%
  mutate(percent = scales::percent(n / sum(n)))
```

Great, with almost no thought at all, we've figured out that Harriet has a 32% chance of of winning, Matila 50% and 18% chance of having the same number of puppies.

Now lets build a quick shiny app to bring this simulation to life.














