---
title: "Eminem Lyric analysis with R"
author: "Ezra Citron"
date: '2021-03-23'
categories: ["R"]
tags: ["R Markdown", "textmining", "NLP"]
editor_options: 
  chunk_output_type: console
draft: true
---

```{r setup, include=FALSE,cache=TRUE}
knitr::opts_chunk$set(collapse = TRUE)
```


# Text Mining with Eminem 

Text mining promises a lot. The ability to get a machine to understand the main topics in a text, or how positive the writer was about the subject could have applications as far reaching as law, analysing survey responces, stock market analysis. I usually favor simplicity over perfection. I'd rather have a 6/10 model that I can interpret and (crucially) explain than a 9/10 model that no one can get their head around. This is why i was so excited when I saw the `tidytext` package from [Julia Sigle](https://juliasilge.com/) at Rstudio. 

I'm going to guide you through a piece a some text analysis, motivating why and how we are extracting insight from pieces of text that would be time consuming (and dull) to read from start to finish. 

## Songs

Songs lyrics are just text. Why not use next generation technology to answer the age old questions of which musicians are the most basic. Good questions lead to good analysis. Here are the questions id like to address.

* Is there a notable difference in laguage used by Artists
* Which words or phrases are idiosyncratic of certain artists.
* Which artists use more complicated laguage (lexical diversity , word length?)

I obviously need to pick a few artists to look at, so, (no judgement pls) i'll go for Queen, Taylor swift, Simon and Garfunkle and Eminem for a varied selection.

The topic of webscraping (downloading the stuff you see on the internet onto your computer in a slighly cleverer way than simply copying and pasting) is an interesting and fun topic, I go though the full process of how I scaped all 395 eminem songs (good luck copying and pasting) from www.azlyrics.com is my blog post will the real scrapy please stand up


# itdf difference between albums
```{r}
library(tidytext)


```


# album 'flow' 

# sentiment over time - is eminem going soft?

# Fastest songs. 
## words per min, sylables per min. Enrich with song length data. 

# Including Plots

You can also embed plots. See Figure \@ref(fig:pie) for example:

```{r pie, fig.cap='A fancy pie chart.', tidy=FALSE}
par(mar = c(0, 1, 0, 1))
pie(
  c(280, 60, 20),
  c('Sky', 'Sunny side of pyramid', 'Shady side of pyramid'),
  col = c('#0292D8', '#F7EA39', '#C4B632'),
  init.angle = -50, border = NA
)
```
