---
title: Upgrade Your Visuals
author: Ezra Citron
date: '2021-03-25'
slug: upgrade-your-visuals
categories: []
tags: []
draft: true
editor_options: 
  chunk_output_type: console
---

This will be a three part series, the first will describe high, level how one can go about upgrading their vis skills, some resources, and packages that we can use. We'll run through an example in a subsequent post. The post is heavily inspired by the work of [Cedric Scherer](https://www.cedricscherer.com/) (I thought i was pretty good before i saw this guy) and posts from [The Pudding](https://pudding.cool/)

## Good, like _really_ good visulisation




```{r}
library(tidyverse)
library(ggsci)
library(showtext)

theme_set(theme_bw(base_size = 5)) # using bases is amazing! do this!

## Loading Google fonts (https://fonts.google.com/)
sysfonts::font_add_google("Gochi Hand", "gochi")
sysfonts::font_add_google("Schoolbell", "bell")
sysfonts::font_add_google(name = "Rubik Mono One")
## Automatically use showtext to render text
showtext_auto()

overall_avg <- mpg %>% summarise(mean(cty)) %>% pull()

(g <- mpg %>% 
  ggplot(aes(cty,hwy,color = class))+
  geom_abline(slope = 0,intercept  = overall_avg,color = 'grey70',size = 1)+
  geom_jitter(position = position_jitter(seed= 2021,height = 20) )+ # didnt know you cuodl set seed here
  scale_x_continuous(expand = c(0.05,0.05))+
    geom_rug(show.legend = F,sides = "tr",size=3,alpha = 0.3)+ # use geom rug, v easy, v cool
    ggsci::scale_color_rickandmorty()+
  labs(x = "City (mpg)",title = "Exapmple of how i might use fonts")+
  theme(title = element_text(family = "Rubik Mono One"),
        legend.text =  element_text(family = "gochi"),
        panel.grid    = element_blank()
        )+
  stat_summary(fun = median,  geom = 'point',color = 'white',size = 3,alpha = 0.6) )
  
g_for_grob <- g+
    theme(line = element_blank(),
          panel.background = element_rect(fill = "transparent"),
          plot.background = element_rect(fill = "transparent", color = "transparent"),
         #panel.border = element_rect(color = "transparent"),
          strip.background = element_rect(color = "gray20"),
          axis.text = element_blank(),
          plot.margin = margin(0, 0, 0, 0),
          legend.position = 'none') +
    labs(x = NULL, y = NULL,title = NULL)

grob_of_g <- ggplot2::ggplotGrob(g_for_grob)

g+annotation_custom(grob = grob_of_g, xmin = 25, xmax = 35, ymin = 0, ymax = 20)

```



going through the cedric scherer tutorial, lets do this, i think i will learn very much 
```{r}
chic <- readr::read_csv("https://raw.githubusercontent.com/Z3tt/R-Tutorials/master/ggplot2/chicago-nmmaps.csv")

```


```{r}
library(patchwork)

g+g/g

my_design <- "
A#CC
A#DD
AB##
AB##
"

g+g+g+g+plot_layout(design = my_design)

```

